High-level cognition is supported by at least second order dynamic correlations in neural activity patterns

### 2019-08-23 paper/main.tex
working on methods

\section*{Methods}
Our general approach to comprises four general steps.  First, we
derive a kernel-based approach to computing dynamic pairwise
correlations in a multivariate timeseries.  Next, we apply a
dimensionality reduction step to \textbf{JRM STOPPED HERE}

>>>>

\section*{Methods}
Our general approach to comprises four general steps.  First, we
derive a kernel-based approach to computing dynamic pairwise
correlations in a $T$ (timepoints) by $K$ (features) multivariate
timeseries, $x_0$.  This yields a $T$ by $\mathcal{O}(K^2)$ matrix of
dynamic correlations, $y_1$, where each row comprises the upper
triangle of the correlation matrix at a single timepoint, reshaped
into a row vector.  Second, we apply a dimensionality reduction step
to project the matrix of dynamic correlations back onto a
$K$-dimensional space.  This yields a $T$ by $K$ matrix, $x_1$, that
reflects an approximation of the dynamic correlations reflected in the
original data.  Third, we use repeated applications of the
kernel-based dynamic correlation step to $x_n$ and the dimensionality
reduction step to the resulting $y_{n+1}$ to estimate high-order
dynamnic correlations.  Each application of these steps to a $T$ by
$K$ time series $x_n$ yields a $T$ by $K$ matrix, $x_{n+1}$, that
reflects the dynamic correlations between the columns of $x_n$.  In
this way, we refer to $n$ as the \textit{order} of the timeseries,
where $x_0$ (order 0) denotes the original data and $x_n$ denotes
$n^\mathrm{th}$-order dynamic correlations between the columns of
$x_0$.  Finally, we use a cross-validation--based decoding approach to
evaluate how well information contained in a given order (or weighted
mixture of orders) may be used to decode relevant cognitive states.
If including a given $x_n$ in the feature set yields higher
classification accuracy on held-out data, we interpret this as
evidence that the given cognitive states are reflected in patterns of
$n^\mathrm{th}$-order correlations.

\textbf{JRM STOPPED HERE}
